Stack Safety as a Security Property

### 2020-07-05 main.tex
Fixed some spots where we weren't using the macros (so MPO and MO wasn't happening)

\definition{Trace Integrity}
\label{def:trace-integrity}
Let $\contour$ be a contour and $MP$ be a (potentially infinite)
$\MPOTRACE$. We will say $MP$ satisfies {\em trace integrity} with
respect to $\contour$ if its final state (if any) agrees with its
initial one on all components marked $\HIGHSEC$ in $\contour$:
%
\[
\mathit{int} ~ \contour ~ MP \triangleq
\left \{ \begin{array}{ll}
  \mathit{True}, & \text{if $MP$ is infinite}\\
  \forall \component. ~ \contour(\component) = \HIGHSEC \rightarrow m_0(\component) = m_f(\component), & \text{otherwise} \\
\end{array}
\right .
\]
\leo{TODO: DISCUSS: Figure out notation for first/last machine state in a trace}

@@

\definition{Stack Integrity}
Let $\callmap$ be a call map and $\codemap$ a code map. We say that a
system satisfies {\em stack integrity} with respect to $\callmap$ and
$\codemap$ if, for every initial machine-policy state pair $(\mach_0,
\pol_0)$ and its induced trace $MP$, and every $n$-transition
$(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$ to a callee $f$ in $MP$,
the prefix $MP_{pre}$ of $MP$ from $(\mach_e, \pol_e)$ until the first
return corresponding to $\mach_c$ (if any) satisfies trace integrity
with respect to the contour at the call:
%
$$\forall MP_{pre}. ~ \mpstate{\mach_e}{\pol_e} \hookrightarrow_P
MP_{pre} ~ | ~ \ret{\mach_c} \rightarrow
\mathit{int}~\mathit{Cof}(\mach_c, f, n)~MP_{pre}$$

@@

\definition{Stack Confidentiality}
Let $\callmap$ be a call map and $\codemap$ a code map. We say that a
system satisfies {\em stack confidentiality} with respect to
$\callmap$ and $\codemap$ if, for every initial machine-policy state
pair $(\mach_0, \pol_0)$ and its induced trace $MP$, and every
$n$-transition $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$ to a callee
$f$ in $MP$, the prefix $MP_{pre}$ of $MP$ from $(\mach_e, \pol_e)$
until the first return corresponding to $\mach_c$ (if any) satisfies
trace integrity with respect to every similarly prefixed machine trace
of every variation $\mach_e'$ with the contour at the call:
$$\forall MP_{pre} ~ M_{pre}. ~
\mpstate{\mach_e}{\pol_e} \hookrightarrow_P MP_{pre} ~ | ~ \ret{\mach_c} \rightarrow$$
$$\forall \mach_e'. ~ \mach_e \approx_{\mathit{Cof}(\mach_c, f, n)} \mach_e' \wedge
\mach_e' \hookrightarrow M_{pre} ~ | ~ \ret{\mach_c} \rightarrow$$
$$\mathit{conf}~\mathit{Cof}(\mach_c, f, n) ~ MP_{pre} ~ M_{pre}$$

>>>>

\definition{Trace Integrity}
\label{def:trace-integrity}
Let $\contour$ be a contour and $\MPT$ be a (potentially infinite)
$\MPOTRACE$. We will say $\MPT$ satisfies {\em trace integrity} with
respect to $\contour$ if its final state (if any) agrees with its
initial one on all components marked $\HIGHSEC$ in $\contour$:
%
\[
\mathit{int} ~ \contour ~ \MPT \triangleq
\left \{ \begin{array}{ll}
  \mathit{True}, & \text{if $\MPT$ is infinite}\\
  \forall \component. ~ \contour(\component) = \HIGHSEC \rightarrow m_0(\component) = m_f(\component), & \text{otherwise} \\
\end{array}
\right .
\]
\leo{TODO: DISCUSS: Figure out notation for first/last machine state in a trace}

@@

\definition{Stack Integrity}
Let $\callmap$ be a call map and $\codemap$ a code map. We say that a
system satisfies {\em stack integrity} with respect to $\callmap$ and
$\codemap$ if, for every initial machine-policy state pair $(\mach_0,
\pol_0)$ and its induced trace $\MPT$, and every $n$-transition
$(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$ to a callee $f$ in $MP$,
the prefix $\MPT_{pre}$ of $\MPT$ from $(\mach_e, \pol_e)$ until the first
return corresponding to $\mach_c$ (if any) satisfies trace integrity
with respect to the contour at the call:
%
$$\forall \MPT_{pre}. ~ \mpstate{\mach_e}{\pol_e} \hookrightarrow_P
\MPT_{pre} ~ | ~ \ret{\mach_c} \rightarrow
\mathit{int}~\mathit{Cof}(\mach_c, f, n)~\MPT_{pre}$$

@@

\definition{Stack Confidentiality}
Let $\callmap$ be a call map and $\codemap$ a code map. We say that a
system satisfies {\em stack confidentiality} with respect to
$\callmap$ and $\codemap$ if, for every initial machine-policy state
pair $(\mach_0, \pol_0)$ and its induced trace $\MPT$, and every
$n$-transition $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$ to a callee
$f$ in $\MPT$, the prefix $\MPT_{pre}$ of $\MPT$ from $(\mach_e, \pol_e)$
until the first return corresponding to $\mach_c$ (if any) satisfies
trace integrity with respect to every similarly prefixed machine trace
of every variation $\mach_e'$ with the contour at the call:
$$\forall \MPT_{pre} ~ \machOT_{pre}. ~
\mpstate{\mach_e}{\pol_e} \hookrightarrow_P \MPT_{pre} ~ | ~ \ret{\mach_c} \rightarrow$$
$$\forall \mach_e'. ~ \mach_e \approx_{\mathit{Cof}(\mach_c, f, n)} \mach_e' \wedge
\mach_e' \hookrightarrow \machOT_{pre} ~ | ~ \ret{\mach_c} \rightarrow$$
$$\mathit{conf}~\mathit{Cof}(\mach_c, f, n) ~ \MPT_{pre} ~ \machOT_{pre}$$
